FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-06-13 paper.tex
More talk draft

\subsection{Tracking more than NaNs}

% This is mostly a stand-in in case we don't get around to adding Inf tracking.
% It should be easy to do, but whether or not we have enough time to do it is
% another matter.
FloatTracker is capable of monitoring all sorts of events in a floating point value's lifetime---not just a value going to NaN.
Extending FloatTracker to handle \texttt{Inf} is just a matter of engineering.
Other values of interest may follow.

>>>>

\subsection{Tracking more than NaNs and Infs}
FloatTracker is capable of monitoring all sorts of events in a floating point value's lifetime---not just a value going to NaN or Inf.
We spent most of the time engineering and testing NaN tracking and injection.
Adding Inf tracking took a few hours.
Adding other values of interest would be issues of relatively simple engineering.
